Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-27 paper/paper.tex
combined best results

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/pub-to-signature}
\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication \glnote{Remove a) and b.}}
\label{fig:signature}
\end{figure}

@@

More specifically, using census data extracted from \citep{rugglesintegrated},
we build a support vector machine classifier (using a linear kernel and
one-versus-all scheme for multi-class classification) for mapping the
 $(1,5)$-TF-IDF representation of an author name to one of the seven ethnic groups. Given a
pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
computed as the estimated probability of $s_1$ to belong to the corresponding
ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
same group. In doing so, the expectation is for the linkage function to become
sensitive to the actual origin of the authors depending on the values of these
features. Indirectly, let us also note that these features hold discriminative
power since if author names are predicted to belong to different ethnic groups,
then they are also likely to correspond to distinct people.

@@

\textit{Combined best settings.} \glnote{todo}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/pub-to-signature}
\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\label{fig:signature}
\end{figure}

@@

More specifically, using census data extracted from \citep{rugglesintegrated},
we build a support vector machine classifier (using a linear kernel and
one-versus-all classification scheme) for mapping the
 $(1,5)$-TF-IDF representation of an author name to one of the seven ethnic groups. Given a
pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
computed as the estimated probability of $s_1$ to belong to the corresponding
ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
same group. In doing so, the expectation is for the linkage function to become
sensitive to the actual origin of the authors depending on the values of these
features. Indirectly, let us also note that these features hold discriminative
power since if author names are predicted to belong to different ethnic groups,
then they are also likely to correspond to distinct people.

@@

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance saturates at $0.9845$, which shows not to be better than the best
reported results ($0.9850$). Since the only difference between these two
solutions is the use of Random Forests instead of GBRT as classifiers, this
result suggests there appears to be no significant gain in using one rather
the other. Both tree-based methods show equally good performance.
